Supporting Information : Extreme climatic events with asymmetric tail-dependence affect population-extinction risk

### 2019-07-16 SuppMat.Rmd
edits, still suppmat fig caption short need to be added
short caption added

\pagenumbering{roman}
\tableofcontents
\listoffigures
\listoftables

@@

<!--Supp. FIG :  age structure model results for C, SC, G, SG with linear model (\Omega = infinity)-->
\begin{figure}[!h]
\begin{center}
\textbf{ \hspace{0.5 cm} (A) \hspace{4.4 cm} (B)} \\
\vspace{-0.2 cm}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_SG_G_linear.pdf}\\
\textbf{ \hspace{0.5 cm} (C) \hspace{4.4 cm} (D)} \\
\vspace{-0.2 cm}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_nonlinear_omg_100.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_SG_G_nonlinear_omg_100.pdf}\\
\caption{Extinction risk (shading represents 95\% confidence interval) from single patch age structured models with time; fecundity of adults and survival of eggs have either left or right tail dependence in their corresponding copula structure. $(A)$ Clayton and Survival Clayton (parameter = 3), $(B)$ Survival Gumbel and Gumbel (parameter = 2.5) for linear model ($\Omega = \infty$), numsims=10000. $(C - D)$ represents the analogous figures as of $(A - B)$ but for non-linear model ($\Omega = 100$). All copula has same Kendall correlation $\tau = 0.6$. \label{fig_extrisk_agestr_C_SC_G_SG_linear}}
\end{center}
\end{figure}

<!--Supp. FIG :  summary : all nonlinear model results for global dispersion : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_global_disp.pdf}
\caption{For each of six nonlinear density-dependence models presented in Table \ref{MT-tab_model_summary} with global dispersal, extinction risk varies as dispersion-rate ($d$) goes from $0$ to $0.5$. Last two columns represent extinction risk calculated for bifurcation parameter $(r)$ taken from under-compensatory and over-compensatory regime of deterministic model analog, respectively.\label{fig_extrisk_allmodel_globaldisp}}
\end{center}
\end{figure}

<!--Supp. FIG : Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_local_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Austin brewer model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Ricker model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with global dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_global_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_risk_global_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with global dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_global_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Austin brewer model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_global_disp.pdf}\\
\caption{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with global dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_global_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

>>>>

\pagenumbering{roman}
\tableofcontents
\listoffigures

@@

<!--Supp. FIG :  age structure model results for C, SC, G, SG with linear model (\Omega = infinity)-->
\begin{figure}[!h]
\begin{center}
\textbf{ \hspace{0.5 cm} (A) \hspace{4.4 cm} (B)} \\
\vspace{-0.2 cm}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_SG_G_linear.pdf}\\
\textbf{ \hspace{0.5 cm} (C) \hspace{4.4 cm} (D)} \\
\vspace{-0.2 cm}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_nonlinear_omg_100.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_SG_G_nonlinear_omg_100.pdf}\\
\caption[Extinction risk from single patch age structured models with time when vital rates have either left (C, SG) or right tail (SC, G) dependence.]{Extinction risk (shading represents 95\% confidence interval) from single patch age structured models with time; fecundity of adults and survival of eggs have either left or right tail dependence in their corresponding copula structure. $(A)$ Clayton and Survival Clayton (parameter = 3), $(B)$ Survival Gumbel and Gumbel (parameter = 2.5) for linear model ($\Omega = \infty$), numsims=10000. $(C - D)$ represents the analogous figures as of $(A - B)$ but for non-linear model ($\Omega = 100$). All copula has same Kendall correlation $\tau = 0.6$. \label{fig_extrisk_agestr_C_SC_G_SG_linear}}
\end{center}
\end{figure}

<!--Supp. FIG :  summary : all nonlinear model results for global dispersion : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_global_disp.pdf}
\caption[Extinction risk vs. dispersal rate for six density dependent metapopulation model with global dispersal.]{For each of six nonlinear density-dependence models presented in Table \ref{MT-tab_model_summary} with global dispersal, extinction risk varies as dispersion-rate ($d$) goes from $0$ to $0.5$. Last two columns represent extinction risk calculated for bifurcation parameter $(r)$ taken from under-compensatory and over-compensatory regime of deterministic model analog, respectively.\label{fig_extrisk_allmodel_globaldisp}}
\end{center}
\end{figure}

<!--Supp. FIG : Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Ricker metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Hassell metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Maynard smith metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_local_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Pennycuick metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Verhulst metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Austin-Brewer model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Austin-Brewer metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Ricker model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_global_disp.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Ricker metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_global_disp.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Hassell metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_global_disp.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Maynard smith metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with global dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_global_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_global_disp.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Pennycuick metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with global dispersal; 
numsims=10000, $\sigma$=1. \label{fig_risk_global_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_global_disp.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Verhulst metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with global dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_global_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Austin brewer model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_global_disp.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Austin-Brewer metapopulation model with global dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with global dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_global_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}
